Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic

### 2021-09-13 psy_peds.Rmd
fixing age bug

```{r}
# Adjusting patient age at the time of visit, assuming the age used is the patients' age at the time of extraction (last discharge date available in the data)
last_data_date <- max(as.Date(demo_raw$last_discharge_date, "%Y-%m-%d"))
clinical_raw <- left_join(clinical_raw, demo_raw[c("patient_num", "cohort", "age")], by = c("patient_num", "cohort"))
clinical_raw$age_time_visit <- clinical_raw$age - floor(as.numeric(last_data_date - as.Date(clinical_raw$calendar_date, dateFormat)) / 365.25)
```

>>>>

```{r}
# Adjusting patient age at the time of visit, assuming the age used is the patients' age at the time of extraction (last discharge date available in the data)
last_data_date <- max(as.Date(demo_raw$last_discharge_date, "%Y-%m-%d"))
clinical_raw <- left_join(clinical_raw, demo_raw[c("patient_num", "cohort", "age")], by = c("patient_num", "cohort"))
clinical_raw$age_time_visit <- clinical_raw$age - floor(as.numeric(last_data_date - as.Date(clinical_raw$calendar_date, dateFormat)) / 365.25)
clinical_raw <- select(clinical_raw, -age)
```
